---
title: "GridSearch"
output: html_document
---

# Table of contents

* [Load Libraries](#libraries)
* [Load Functions](#functions)
    + [Scaling Functions](#scaling)
    + [Classification Function](#classification)
    + [Evaluation Functions](#evaluation)
    + [Validation Functions](#validation)
    + [Wrapper Functions](#wrapper)
#Load libraries and sources
```{r}
options(warn=-1)

library(knitr)
library(mlbench)
library(lattice)
library(ggplot2)
library(caret)
library(MASS)
library(class)
library(e1071)
library(cluster)
library(clValid)
library(xgboost)
suppressMessages(library(gplots))
suppressMessages(library(randomForest))
suppressMessages(library(gbm))
suppressMessages(library(combinat))
suppressMessages(library(glmnet))

options(warn=0)
```

# Load sources
```{r}
source("R/paths.R")
source("R/prediction.R")
source("R/selection.R")
source("R/validation.R")
source("R/evaluation.R")

```

#Load params
```{r search-params}

kinase_classes <- c('Akt', 'mTOR')
feature_sets <- c('temporal', 'relative', 'retained', 'final')
feature_sets <- c('final')
ensemble_size <- seq(0, 100, 25)[-1]
negative_size <- c(1, 1.1, 1.2)
bmm_threshold <- seq(0, 1, 0.01)
model_type <- c('svm', 'glm', 'xgb', 'rf')
svm_kernel <- c('radial')
svm_cost <- c(0, 0.5, 1, 2)
glm_family <- c('binomial', 'gaussian')
glm_alpha <- c(0, 1)
glm_lambda <- 10^seq(10, -2, length = 100)
xgb_nrounds <- c(10, 15, 25, 50)
xgb_depth <- c(2, 3, 4)
rf_ntree <- c(10, 20, 50, 100)
rf_nodesize <- c(4, 6, 8)
estimate_c <- c(TRUE, FALSE)

full_data <- get_dataset()
full_data <- cbind(full_data, hclust_features)
features <- get_features(full_data)
kinases <- kinase_idx(kinase_classes)

```

# Generate probabilities: Model 1 --> Random Forest
``` {r end-to-end}

prob_df <- full_data[, c('Identifier', 'Seq.Window')]

for(k in c('Akt', 'mTOR')){
  
  k_pred <- get_prediction(
  kinase = k,
  kinases = kinases,
  full_dataset = full_data[, features$final],
  test_idx = 1,
  ensemble_size = 100,
  negative_size = floor(length(kinases[[k]][['positive-idx']]) * 1),
  model_type = 'rf',
  svm_kernel = NULL,
  svm_cost = NULL,
  glm_family = NULL,
  glm_alpha = NULL,
  xgb_rounds = NULL,
  xgb_depth = NULL,
  rf_ntree = 100,
  rf_nodesize = 2,
  estimate_c = FALSE,
  other_ksr = FALSE
  )
  
  prob_df <- cbind(prob_df, k_pred$prediction_full)
  
}

colnames(prob_df) <- c('Identifier', 'Seq.Window', 'Akt_pred', 'mTOR_pred')

write.csv(prob_df, file='probability_results_rf.csv')
```

# Generate probabilities: Model 2 --> SVM
``` {r end-to-end}

prob_df <- full_data[, c('Identifier', 'Seq.Window')]

for(k in c('Akt', 'mTOR')){
  
  k_pred <- get_prediction(
  kinase = k,
  kinases = kinases,
  full_dataset = full_data[, features$final],
  test_idx = 1,
  ensemble_size = 100,
  negative_size = floor(length(kinases[[k]][['positive-idx']]) * 1),
  model_type = 'svm',
  svm_kernel = 'radial',
  svm_cost = 1,
  glm_family = NULL,
  glm_alpha = NULL,
  xgb_rounds = NULL,
  xgb_depth = NULL,
  rf_ntree = NULL,
  rf_nodesize = NULL,
  estimate_c = TRUE,
  other_ksr = FALSE
  )
  
  prob_df <- cbind(prob_df, k_pred$prediction_full)
  
}

colnames(prob_df) <- c('Identifier', 'Seq.Window', 'Akt_pred', 'mTOR_pred')

write.csv(prob_df, file='probability_results_svm.csv')
```

# Generate probabilities: Model 3 --> XGBoost
``` {r end-to-end}

prob_df <- full_data[, c('Identifier', 'Seq.Window')]

for(k in c('Akt', 'mTOR')){
  
  k_pred <- get_prediction(
  kinase = k,
  kinases = kinases,
  full_dataset = full_data[, features$final],
  test_idx = 1,
  ensemble_size = 100,
  negative_size = floor(length(kinases[[k]][['positive-idx']]) * 1),
  model_type = 'xgb',
  svm_kernel = NULL,
  svm_cost = NULL,
  glm_family = NULL,
  glm_alpha = NULL,
  xgb_rounds = 100,
  xgb_depth = 4,
  rf_ntree = NULL,
  rf_nodesize = NULL,
  estimate_c = FALSE,
  other_ksr = FALSE
  )
  
  prob_df <- cbind(prob_df, k_pred$prediction_full)
  
}

colnames(prob_df) <- c('Identifier', 'Seq.Window', 'Akt_pred', 'mTOR_pred')

write.csv(prob_df, file='probability_results_xgb.csv')
```

# Generate probabilities: Model 4 --> Logistic Regression (Lasso)
``` {r end-to-end}

prob_df <- full_data[, c('Identifier', 'Seq.Window')]

for(k in c('Akt', 'mTOR')){
  
  k_pred <- get_prediction(
  kinase = k,
  kinases = kinases,
  full_dataset = full_data[, features$temporal],
  test_idx = 1,
  ensemble_size = 100,
  negative_size = floor(length(kinases[[k]][['positive-idx']]) * 1),
  model_type = 'glm',
  svm_kernel = NULL,
  svm_cost = NULL,
  glm_family = 'binomial',
  glm_alpha = 1,
  xgb_rounds = NULL,
  xgb_depth = NULL,
  rf_ntree = NULL,
  rf_nodesize = NULL,
  estimate_c = TRUE,
  other_ksr = FALSE
  )
  
  prob_df <- cbind(prob_df, k_pred$prediction_full)
  
}

colnames(prob_df) <- c('Identifier', 'Seq.Window', 'Akt_pred', 'mTOR_pred')

write.csv(prob_df, file='probability_results_glm.csv')
```

# Ensemble voting
```{r}

get_akt_probs <- function(){
  print('test')
}


```

# Grid Search
``` {r}

output_df <- 0
iter <- 0
for(f in feature_sets) {
  data <- full_data[, features[[f]]]
  for(k in kinase_classes){
    for(e in ensemble_size){
      for(n in negative_size){
        for(ec in estimate_c){
          for(kt in svm_kernel){
            for(kc in svm_cost){
              
              print(paste(
                'features: ', f,
                'kinase: ', k, 
                'ensembles: ', e, 
                'negative: ', n, 
                'estim c:', FALSE,
                'svm_kernel: ', kt, 
                'svm_cost: ', kc
                ))
              
              start_time <- Sys.time()
              
              p <- LOOCV_KSR_probabilities(
                kinase = k,
                kinases = kinases,
                full_dataset = data,
                ensemble_size = e,
                floor(length(kinases[[k]][['positive-idx']]) * n),
                model_type = 'svm',
                svm_kernel = kt,
                svm_cost = kc,
                glm_family = NULL,
                glm_alpha = NULL,
                xgb_rounds = NULL,
                xgb_depth = NULL,
                rf_ntree = NULL,
                rf_nodesize = NULL,
                estimate_c = ec
                )
  
              run_time <- as.numeric(Sys.time() - start_time)
  
              for(b in bmm_threshold){
                
                output_list <- list()
                output_list$bmm_threshold <- b
                output_list$kinase <- k
                output_list$model_type <- 'svm'
                output_list$estimated_c <- ec
                output_list$svm_kernel <- kt
                output_list$svm_cost <- kc
                output_list$glm_family <- NULL
                output_list$glm_alpha <- NULL
                output_list$xgb_rounds <- NULL
                output_list$xgb_depth <- NULL
                output_list$rf_ntree <- NULL
                output_list$rf_nodesize <- NULL

                output_bmm <- LOOCV_KSR_thr_bmm(k, kinases, b, data, p)
                output_bmm$confusion_matrix <- NULL
                
                output_list <- c(output_list, output_bmm)
                output_list$feature_set <- f
                output_list$ensemble_size <- e
                output_list$negative_size <- floor(length(kinases[[k]][['positive-idx']]) * n)
                output_list$runtime <- run_time
  
                output_list <- as.data.frame(output_list)
  
                if(is.numeric(output_df)) { output_df <- output_list }
                else { output_df <- rbind(output_df, output_list)}
  
              }
  
              iter <- iter + 1
              print(paste('iteration: ',iter, ' run time: ', run_time))
            }
          }
        }
      }
    }
  }
}

write.csv(output_df, file='grid_search_results_svm_final.csv')

```